A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-28 manuscript.Rmd
new text for conceptual section

In the remainder of this section, we will briefly explain why each of these four building blocks is needed and how it plays a role in guaranteeing reproducibility.
To resolve ambiguity across multiple versions of code and data that may be come into existence during the development phase of a research project, we recommend the use of a version control system.
A version control system tracks changes to all project-related files (e.g., materials, data, and code) over time.
At a later stage, single files or the entire project can be compared to or reverted to an earlier version.
Additional features such as branches allow parallel versions to exist that can be merged later.
Specific snapshots of a repository can be marked, such that one can clearly label a given project status as the one that created a given preregistration, a given preprint, or the final authors' version accepted at a journal.
Using version control protects against loss of files and also supports remote collaboration with semi-automated tools for tracking and merging changes.

@@

>>>>

The remainder of this section briefly explains why each of these four building blocks is needed and the role they play in ensuring reproducibility.

First, to resolve ambiguity across multiple versions of code and data that may be come into existence during the development phase of a research project, we recommend the use of a version control system.
A version control system tracks changes to all project-related files (e.g., materials, data, and code) over time.
At a later stage, single files or the entire project can be compared to or reverted to an earlier version.
Additional features such as branches allow parallel versions to exist that can be merged later.
Specific snapshots of a repository can be marked, such that one can clearly label a given project status as the one that created a given preregistration, a given preprint, or the final authors' version accepted at a journal.
Using version control protects against loss of files and also supports remote collaboration with semi-automated tools for tracking and merging changes.

@@

One would hope that sharing a literate statistical analysis would allow others (including one own's future self) to simply download and run (ie., reproduce) a given analysis. 
However, as @ argue, in most instances this approach fails. 
In practice, dependencies on external software (such as system libraries or components of the programming language) are frequently unmentioned and the components or packages are not included. Troubleshooting  issues specific to a certain programming language or dependent tool typically requires considerable expertise and hinder reproducibility. 
One solution to this problem is to provide not only the analysis script but all dependent software packages and system libraries in a so-called _container_. "By packaging the key elements of the computational  environment  needed  to  run  the  desired  software, [...] they  make the software much easier to use, and the results easier to reproduce [@silver2017].
Instead of leaving it to the user which software should be installed how on their computer, Docker provides all software used in an analysis, including the operating system itself.
The operating system level is important because some functionality may be passed to software layers beneath the programming language, such as calls to random number generators, linear algebra libraries and such.
Docker does this without interfering with the already installed software by using a virtual software environment that is independent of the host software environment.
Such a snapshot of the software stack is called an "image".
Packaging all needed software in such an image requires considerable amounts of storage space.
There are two major strategies helping to keep the storage requirements reasonable.
First, there is a community that maintains images for particular purposes.
For example, there are ready-made images for R, based on Ubuntu (a Linux operating system) containers [@boettigerIntroductionRockerDocker2017].
Users can then install whatever they need in addition to what is provided by these pre-compiled images.
`r ifelse(is.na(container_size), "", glue::glue("The image that was used for this article uses {round(container_size, 2)}Gb of disc space."))`
Our image includes Ubuntu, R, R Studio, LaTeX as well as a variety of R packages like the tidyverse [@tidyverse], amounting to `r installed.packages() %>% as.data.frame() %>% filter(is.na(Priority)) %>% nrow()` packages.
Second, instead of saving a binary image of the software, one can also save a container recipe, a so-called  `Dockerfile`.
This recipe is a textual description of all commands that need to be executed to recreate the image.
Such files are tiny (the `r link("https://github.com/aaronpeikert/repro-tutorial/blob/main/Dockerfile", "Dockerfile")` for this project is `r round(as.numeric(fs::file_size("Dockerfile"))/1024^1, 2)`Kb big) and are an unambiguous description of how to recreate a given container image.
However, they rely on the assumption that all software repositories will remain accessible and will continue to make available historic software versions.
For archiving, we therefore recommend that a full image is always kept (see Section on [Archiving Docker]).
With the `repro`-package adding R packages dependencies is as simple as adding them to the header under the tag `packages:`

The fourth and last concept we rely on is 
In software projects, tools like the make utility, are used to automatically determine, which pieces of a program need to be recompiled when the source code or dependent libraries are changed and also to issue the commands how to build the final product. In essence, developers provide a single _Makefile_, which can be thought of as a collection of computational recipes. Similar to a collection of cooking recipes, we can have multiple products (_targets_ in Make speak) with different ingredients (_requirements_) and different steps of preparation (_recipe_). In the context of a scientific data analysis, the targets are typically the final scientific report (e.g., the one to be submitted to a journal) and possibly intermediate results, such as preprocessed data files, simulation results, analysis results). To make this more concrete, consider the following hypothetical example, in which a research project contains a script to simulate data (`simulate.R`) and a scientific report of the simulation results written in R Markdown (`manuscript.Rmd`). A Makefile could then look like this:

```
manuscript.pdf: manuscript.Rmd simulation_results.csv 
  Rscript -e 'rmarkdown::render("manuscript.Rmd")'

simulation_results.csv: simulate.R
  Rscript -e 'source("simulate.R")'
```

There are two targets, the final rendered report (`manuscript.pdf`, l.1) and the simulation results (`simulation_results.csv`, l.4). Each target is followed by a colon and a list of requirements. If a requirement is  newer than the target, the recipe will be executed to rebuild the target.  If a requirement does not exist, Make seeks to find a recipe to build the requirement first before building the target. Here, if one were to build the final `manuscript.pdf` by rendering the R Markdown with the command shown in l.2, Make would make sure that the file `simulation_results.csv` exists; if not, it would find that this is also a target and issue the command in l.5 to run the simulation first before rendering the manuscript. This way, we ensure that the simulation is always run before the manuscript is built and that the manuscript is rebuilt if the simulation code was changed. <!-- AP: I was just wondering... is this true? Is the caching mechanism transitive?-->

To summarize, the workflow by @Peikert2019 requires four components, dynamic document generation (using R Markdown), version control (using Git), internal dependency management (using Make), containerization (using Docker). While R Markdown and git are well integrated into the R environment through R Studio, Make and Docker require a level of expertise that is often beyond the training of scholars outside studies of information technology, which represents a considerable hurdle in the acceptance and implementation of the workflow. To remove this hurdle, we have developed a new R package `repro` that supports scholars in setting up, maintaining, and reproducing research projects in R. In the remainder, we will walk you through a complete research project, from sketching the very first idea over preregistration, data analysis, and submission of a preprint while focusing on how the `repro`-package enables users to maintain reproducibility of all steps.
